\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-15 foci/paper.tex
Minor edits

\section{Introduction}
Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.  A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of Internet users have tried to become more anonymous online~\cite{pew}.  Despite this, users do not believe that they have the tools to solve this problem.

In December of 2013, the cloud storage company, Pogoplug, released the Safeplug, which is a small box that plugs into a user's home router.  It claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.  We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, network behavior, and usability of the device.  The following are some of our findings:

@@

Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users. However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle, which can be used free of charge.  In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.  We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.

@@

First, we activated the device by following simple instructions.  Next, we followed the configuration instructions based on our specific platform and browser (the options are shown in Table \ref{table_example}) to set up the Safeplug as our browser's HTTP proxy.  The last step was to modify the settings; this page is shown in Figure~\ref{fig:settings}.  We can turn Tor on/off, turn ad-blocking on/off, and turn relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).  Additionally, we can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.

@@

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

@@

The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.  For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.  This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{enumerate} \setlength{\itemsep}{.2mm}
\item Set up a web page with the JavaScript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is off.  
\end{enumerate}

@@

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.  It is critical for Safeplug to correct their security errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

>>>>

\section{Introduction}
Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to tracking, surveillance, and theft of their data.  A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of Internet users have tried to become more anonymous online~\cite{pew}.  Despite this, users do not believe that they have the tools to solve this problem.

In December 2013, the cloud storage company Pogoplug released the Safeplug, a small box that plugs into a user's home router.  It claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online by routing all traffic through Tor~\cite{safeplug}.  We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, network behavior, and usability of the device.  The following are some of our findings:

@@

Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users. However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle, which can be used free of charge.  In order to determine if the Safeplug provides value to users, we measure the privacy implications between the different technologies.  We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.

@@

First, we activated the device by following simple instructions.  Next, we followed the configuration instructions based on our specific platform and browser (the options are shown in Table \ref{table_example}) to set up the Safeplug as our browser's HTTP proxy.  The last step was to modify the settings; this page is shown in Figure~\ref{fig:settings}.  We can turn Tor on/off, turn ad-blocking on/off, and turn Tor relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).  Additionally, we can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.

@@

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

@@

The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.  For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease and better protects privacy.  This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & Third Party JavaScript & Third Party Flash & Third Party Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{enumerate} \setlength{\itemsep}{.2mm}
\item Set up a web page with the JavaScript code, which will send the POST request of the following format to all addresses in the common ranges: \url{http://<IP address>/svc/xspctrl/disableTor}.
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her Safeplug settings page to learn that Tor is off.  
\end{enumerate}

@@

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.  It is critical for Safeplug to correct their security errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online would be better served by the Tor Browser Bundle.
